Brownian Dynein Model

### 2016-04-02 latex/derivation.tex
Add some new BOTHBOUND code. Code doesn't compile, but is getting there. Add new struct members, change how dynein_walk handles BOTHBOUND, change the way forces are stored to use BOTHBOUND names, some other changes as well.
Add incomplete bothbound velocity equations to dynein_struct_bothbound.cpp. Incomplete!

\begin{align}
  \dot{\Theta_{1}} &= \frac{1}{\sqrt{1-\left(\frac{L^2+L_{n}^2-L_{f}^2}{2LL_{n}}\right)^2}}\left(\frac{2L_n\dot{L_n} - 2L_f\dot{L_f}}{2LL_n}\right)\left(\frac{L^2+L_n^2-L_f^2}{-2LL_n^2\dot{L_n}}\right)\\
  \dot{\Theta_{2}} &= \pm \frac{1}{\sqrt{1-\left(\frac{L_{s}^2+L_{n}^2-L_{t}^2}{2L_{s}L_{n}}\right)^2}}\left(\frac{L_n\dot{L_n}}{L_s}\right)\left(\frac{L_s^2+L_{n}^2-L_t^2}{-2L_sL_n^2\dot{L_n}}\right)\\
\end{align}

@@

\begin{align}  
  \dot{X}_{bm} = \hspace{1cm}& \frac{1}{\gamma} \Big(F_{xml} + \mn \lambda_{bs}(X_{bm} - X_{bb}) + \lambda_{bt}(X_{t } - X_{bm}) \Big) + R_{xml}  &= A_{nx}\dot{L}_n + A_{fx}\dot{L}_f\\
  \dot{X}_{t } = \hspace{1cm}& \frac{1}{\gamma} \Big(F_{xt } + \mn \lambda_{bt}(X_{t } - X_{bm}) + \lambda_{ft}(X_{fm} - X_{t }) \Big) + R_{xt } &= B_{xn}\dot{L}_n + B_{xf}\dot{L}_f\\
  \dot{X}_{fm} = \hspace{1cm}& \frac{1}{\gamma} \Big(F_{xmr} + \mn \lambda_{ft}(X_{fm} - X_{t }) + \lambda_{fs}(X_{fb} - X_{fm}) \Big) + R_{xmr} &= C_{xn}\dot{L}_n + C_{xf}\dot{L}_f
\end{align}

\begin{align}  
  \dot{Y}_{bm} &= \hspace{1cm} \frac{1}{\gamma} \Big(F_{yml} + \mn \lambda_{bs}(Y_{bm} - Y_{bb}) + \lambda_{bt}(Y_{t } - Y_{bm}) \Big) + R_{yml} &= A_{yn}\dot{L}_n + A_{yf}\dot{L}_f\\
  \dot{Y}_{t}  &= \hspace{1cm} \frac{1}{\gamma} \Big(F_{yt } + \mn \lambda_{bt}(Y_{t } - Y_{bm}) + \lambda_{ft}(Y_{fm} - Y_{t }) \Big) + R_{yt } &= B_{yn}\dot{L}_n + B_{yf}\dot{L}_f\\
  \dot{Y}_{fm} &= \hspace{1cm} \frac{1}{\gamma} \Big(F_{ymr} + \mn \lambda_{ft}(Y_{fm} - Y_{t }) + \lambda_{fs}(Y_{fb} - Y_{fm}) \Big) + R_{ymr} &= C_{yn}\dot{L}_n + C_{yf}\dot{L}_f
\end{align}

>>>>

\begin{align}
  \dot{\Theta_1} &= \frac{-1}{\sqrt{1-\left(\frac{L^2+L_{n}^2-L_{f}^2}{2LL_{n}}\right)^2}}\left(\frac{2L_n\dot{L_n} - 2L_f\dot{L_f}}{2LL_n} - \frac{L^2+L_n^2-L_f^2}{2LL_n^2}\dot{L_n}\right)\\
  \dot{\Theta_2} &= \mp \frac{1}{\sqrt{1-\left(\frac{L_{s}^2+L_{n}^2-L_{t}^2}{2L_{s}L_{n}}\right)^2}}\left(\frac{\dot{L}_n}{L_s} - \frac{L_s^2+L_{n}^2-L_t^2}{2L_sL_n^2\dot{L_n}}\right)\\
\end{align}

@@

\begin{align}  
  \dot{X}_{nm} = \hspace{1cm}& \frac{1}{\gamma} \Big(F_{xml} + \mn \lambda_{bs}(X_{bm} - X_{bb}) + \lambda_{bt}(X_{t } - X_{bm}) \Big) + R_{xml}  &= A_{nx}\dot{L}_n + A_{fx}\dot{L}_f\\
  \dot{X}_{t } = \hspace{1cm}& \frac{1}{\gamma} \Big(F_{xt } + \mn \lambda_{bt}(X_{t } - X_{bm}) + \lambda_{ft}(X_{fm} - X_{t }) \Big) + R_{xt } &= B_{xn}\dot{L}_n + B_{xf}\dot{L}_f\\
  \dot{X}_{fm} = \hspace{1cm}& \frac{1}{\gamma} \Big(F_{xmr} + \mn \lambda_{ft}(X_{fm} - X_{t }) + \lambda_{fs}(X_{fb} - X_{fm}) \Big) + R_{xmr} &= C_{xn}\dot{L}_n + C_{xf}\dot{L}_f
\end{align}

\begin{align}  
  \dot{Y}_{nm} &= \hspace{1cm} \frac{1}{\gamma} \Big(F_{yml} + \mn \lambda_{bs}(Y_{bm} - Y_{bb}) + \lambda_{bt}(Y_{t } - Y_{bm}) \Big) + R_{yml} &= A_{yn}\dot{L}_n + A_{yf}\dot{L}_f\\
  \dot{Y}_{t}  &= \hspace{1cm} \frac{1}{\gamma} \Big(F_{yt } + \mn \lambda_{bt}(Y_{t } - Y_{bm}) + \lambda_{ft}(Y_{fm} - Y_{t }) \Big) + R_{yt } &= B_{yn}\dot{L}_n + B_{yf}\dot{L}_f\\
  \dot{Y}_{fm} &= \hspace{1cm} \frac{1}{\gamma} \Big(F_{ymr} + \mn \lambda_{ft}(Y_{fm} - Y_{t }) + \lambda_{fs}(Y_{fb} - Y_{fm}) \Big) + R_{ymr} &= C_{yn}\dot{L}_n + C_{yf}\dot{L}_f
\end{align}

### 2016-04-02 latex/paper.tex
Add incomplete bothbound velocity equations to dynein_struct_bothbound.cpp. Incomplete!

\begin{align}
  \frac{dX_{nm}}{dL_n} &= L_s\Big(
  \cos\theta_n\frac{d\cos\theta_{ns}}{dL_n}
  + \cos\theta_{ns}\frac{d\cos\theta_{n}}{dL_n} \\
  &- \sin\theta_n\frac{d\sin\theta_{ns}}{dL_n}
  - \sin\theta_{ns}\frac{d\sin\theta_{n}}{dL_n}
  \Big)\\
\end{align}
\begin{multline}
  \frac{dY_{nm}}{dL_n} = L_s\Big(
  \cos\theta_n\frac{d\sin\theta_{ns}}{dL_n}
  + \sin\theta_{ns}\frac{d\cos\theta_{n}}{dL_n} \\
  + \sin\theta_n\frac{d\cos\theta_{ns}}{dL_n}
  + \cos\theta_{ns}\frac{d\sin\theta_{n}}{dL_n}
  \Big)
\end{multline}

\begin{multline}
  \frac{dX_{nm}}{dL_f} = L_s\Big(
  \cos\theta_n\frac{d\cos\theta_{ns}}{dL_f}
  + \cos\theta_{ns}\frac{d\cos\theta_{n}}{dL_f} \\
  - \sin\theta_n\frac{d\sin\theta_{ns}}{dL_f}
  - \sin\theta_{ns}\frac{d\sin\theta_{n}}{dL_f}
  \Big)
\end{multline}
\begin{multline}
  \frac{dY_{nm}}{dL_f} = L_s\Big(
  \cos\theta_n\frac{d\sin\theta_{ns}}{dL_f}
  + \sin\theta_{ns}\frac{d\cos\theta_{n}}{dL_f} \\
  + \sin\theta_n\frac{d\cos\theta_{ns}}{dL_f}
  + \cos\theta_{ns}\frac{d\sin\theta_{n}}{dL_f}
  \Big)
\end{multline}

@@

which we apply our coordinate derivatives to and get:

\begin{align}
  \frac{dX_{nm}}{dL_n} &= L_s\Big(
  \cos\theta_n\left(\frac{1}{L_s} - \frac{L_s^2 + L_n^2 - L_t^2}{2L_sL_n^2}\right)\\
  &+ \cos\theta_{ns}\left(\frac{1}{L} - \frac{L^2 + L_n^2 - L_f^2}{2L L_n^2}\right)\\
  &- \sin\theta_n\frac{-\cos\theta_n}{\sqrt{1-\cos^2\theta_n}}
  \left(\frac{1}{L} - \frac{L^2 + L_n^2 - L_f^2}{2L L_n^2}\right)\\
  &\pm \sin\theta_{ns}
    \frac{\cos\theta_{ns}}{\sqrt{1-\cos^2\theta_{ns}}}
    \left(\frac{1}{L_s} - \frac{L_s^2+L_n^2-L_t^2}{2LL_n^2}\right)
  \Big)
\end{align}

which we can apply the chain rule to using:

\begin{align}
  \dot{Y}_{nm} = \frac{\partial Y_{nm}}{\partial L_n} \dot{L_n}
  +  \frac{\partial Y_{nm}}{\partial L_{f}} \dot{L_{f}}
\end{align}
and correspondingly for the $X$ formula.  So that now the interesting
things to compute in order to relate the time derivatives of $L_n$ and
$L_f$ to that of $Y_{nm}$ can easily be expressed in terms of these
partial derivatives with respect to the lengths $L_n$ and $L_f$.  This
gives us something like
\begin{multline}
  \frac{\partial X_{nm}}{\partial L_n} = L_s\Bigg(
  \cos\theta_n\frac{\partial \cos\theta_{ns}}{\partial L_n}
  + \cos\theta_{ns}\frac{\partial \cos\theta_{n}}{\partial L_n} \\
  - \sin\theta_n\frac{\partial \sin\theta_{ns}}{\partial L_n}
  - \sin\theta_{ns}\frac{\partial \sin\theta_{n}}{\partial L_n}
  \Bigg)
\end{multline}
However, the $\sin$s of our angles are expressed in terms of the
cosines, so we will (in practice) want to make use of the fact that
\begin{align}
  \frac{\partial \sin\theta_{n}}{\partial L_n} &=
  \frac{d \sin\theta_{n}}{d \cos\theta_n}
  \frac{\partial \cos\theta_{n}}{\partial L_n} \\
  &=
  -\frac{\cos\theta_{n}}{\sin\theta_n}
  \frac{\partial \cos\theta_{n}}{\partial L_n}
\end{align}
Using this we could imagine simplifying our former equation using this
expression for $\frac{\partial \sin\theta_{n}}{\partial L_n}$, but
that would only make it harder to read and check.  Let's keep all
chain rules and derivatives as explicit as possible!

The
corresponding C++ code could look like:
\begin{verbatim}
  dXnm_dLn = Ls*(cosAn*dcosAns_dLn
                 + cosAns*dcosAn_dLn
                 - sinAn*dsinAns_dLn
                 - sinAns*dsinAn_dLn);
\end{verbatim}
Basically, we have lots of chain rules.

>>>>

\begin{multline}
  \frac{dX_{nm}}{dL_n} = L_s\Big(
  \cos\theta_n\frac{d\cos\theta_{ns}}{dL_n}
  + \cos\theta_{ns}\frac{d\cos\theta_{n}}{dL_n} \\
  - \sin\theta_n\frac{d\sin\theta_{ns}}{dL_n}
  - \sin\theta_{ns}\frac{d\sin\theta_{n}}{dL_n}
  \Big)\\
\end{multline}

\begin{multline}
  \frac{dY_{nm}}{dL_n} = L_s\Big(
  \cos\theta_n\frac{d\sin\theta_{ns}}{dL_n}
  + \sin\theta_{ns}\frac{d\cos\theta_{n}}{dL_n} \\
  + \sin\theta_n\frac{d\cos\theta_{ns}}{dL_n}
  + \cos\theta_{ns}\frac{d\sin\theta_{n}}{dL_n}
  \Big)
\end{multline}

\begin{multline}
  \frac{dX_{nm}}{dL_f} = L_s\Big(
  \cos\theta_n\frac{d\cos\theta_{ns}}{dL_f}
  + \cos\theta_{ns}\frac{d\cos\theta_{n}}{dL_f} \\
  - \sin\theta_n\frac{d\sin\theta_{ns}}{dL_f}
  - \sin\theta_{ns}\frac{d\sin\theta_{n}}{dL_f}
  \Big)
\end{multline}

\begin{multline}
  \frac{dY_{nm}}{dL_f} = L_s\Big(
  \cos\theta_n\frac{d\sin\theta_{ns}}{dL_f}
  + \sin\theta_{ns}\frac{d\cos\theta_{n}}{dL_f} \\
  + \sin\theta_n\frac{d\cos\theta_{ns}}{dL_f}
  + \cos\theta_{ns}\frac{d\sin\theta_{n}}{dL_f}
  \Big)
\end{multline}

@@

The corresponding C++ code could look like:
\begin{verbatim}
  dXnm_dLn = Ls*(cosAn*dcosAns_dLn
                 + cosAns*dcosAn_dLn
                 - sinAn*dsinAns_dLn
                 - sinAns*dsinAn_dLn);
\end{verbatim}
Basically, we have lots of chain rules.\\

We then create a system of equations by equating velocities from Brownian dynamics to the velocities
we derived above:

\onecolumn

\begin{align}
  \dot{X}_{nm} = \hspace{1cm}& \frac{1}{\gamma} \Big(F_{xml} + \mn \lambda_{bs}(X_{bm} - X_{bb})
  + \lambda_{bt}(X_{t } - X_{bm}) \Big) + R_{xml}
  &= \frac{X_{nm}}{Ln}\dot{L}_n + \frac{X_{nm}}{Lf}\dot{L}_f\\
  \dot{X}_{t } = \hspace{1cm}& \frac{1}{\gamma} \Big(F_{xt } + \mn \lambda_{bt}(X_{t } - X_{bm})
  + \lambda_{ft}(X_{fm} - X_{t }) \Big) + R_{xt }
  &= \frac{X_{t}}{Ln}\dot{L}_n + \frac{X_{t}}{Lf}\dot{L}_f\\
  \dot{X}_{fm} = \hspace{1cm}& \frac{1}{\gamma} \Big(F_{xmr} + \mn \lambda_{ft}(X_{fm} - X_{t })
  + \lambda_{fs}(X_{fb} - X_{fm}) \Big) + R_{xmr}
  &= \frac{X_{fm}}{Ln}\dot{L}_n + \frac{X_{fm}}{Lf}\dot{L}_f
\end{align}

\begin{align}
  \dot{Y}_{nm} &= \hspace{1cm} \frac{1}{\gamma} \Big(F_{yml} + \mn \lambda_{bs}(Y_{bm} - Y_{bb})
  + \lambda_{bt}(Y_{t } - Y_{bm}) \Big) + R_{yml}
  &= \frac{Y_{nm}}{Ln}\dot{L}_n + \frac{Y_{nm}}{Lf}\dot{L}_f\\
  \dot{Y}_{t}  &= \hspace{1cm} \frac{1}{\gamma} \Big(F_{yt } + \mn \lambda_{bt}(Y_{t } - Y_{bm})
  + \lambda_{ft}(Y_{fm} - Y_{t }) \Big) + R_{yt }
  &= \frac{Y_{t}}{Ln}\dot{L}_n + \frac{Y_{t}}{Lf}\dot{L}_f\\
  \dot{Y}_{fm} &= \hspace{1cm} \frac{1}{\gamma} \Big(F_{ymr} + \mn \lambda_{ft}(Y_{fm} - Y_{t })
  + \lambda_{fs}(Y_{fb} - Y_{fm}) \Big) + R_{ymr}
  &= \frac{Y_{fm}}{Ln}\dot{L}_n + \frac{Y_{fm}}{Lf}\dot{L}_f
\end{align}

\section{Matrix Solution via Mathematica}
Here we convert the above system into matrix form, solve it in Mathematica and list the results.

\[
\begin{pmatrix}
  -\frac{X_{nm}}{Ln} & -\frac{X_{nm}}{Lf}
  & -\frac{X_{bm}-X_{bb}}{\gamma} & \frac{X_{t}-X_{bm}}{\gamma} & 0 & 0\\
  -\frac{X_{t}}{Ln} & -\frac{X_{t}}{Lf}
  & 0 & -\frac{X_{t}-X_{bm}}{\gamma} & \frac{X_{fm}-X_{t}}{\gamma} & 0\\
  -\frac{X_{fm}}{Ln} & -\frac{X_{fm}}{Lf}
  & 0 & 0 & -\frac{X_{fm}-X_{t}}{\gamma} & \frac{X_{fb}-X_{fm}}{\gamma}\\
  -\frac{Y_{nm}}{Ln} & -\frac{Y_{nm}}{Lf}
  & -\frac{Y_{bm}-Y_{bb}}{\gamma} & \frac{Y_{t}-Y_{bm}}{\gamma} & 0 & 0\\
  -\frac{Y_{t}}{Ln} & -\frac{Y_{t}}{Lf}
  & 0 & -\frac{Y_{t}-Y_{bm}}{\gamma} & \frac{Y_{fm}-Y_{t}}{\gamma} & 0\\
  -\frac{Y_{fm}}{Ln} & -\frac{Y_{fm}}{Lf}
  & 0 & 0 & -\frac{Y_{fm}-Y_{t}}{\gamma} & \frac{Y_{fb}-Y_{fm}}{\gamma}\\
\end{pmatrix}
\begin{pmatrix}
  \dot{L}_n\\
  \dot{L}_f\\
  \lambda_{bs}\\
  \lambda_{bt}\\
  \lambda_{ft}\\
  \lambda_{fs}\\
\end{pmatrix}
=
\begin{pmatrix}
  -\frac{F_{xml}}{\gamma} - R_{xml}\\
  -\frac{F_{xt}}{\gamma} - R_{xt}\\
  -\frac{F_{xmr}}{\gamma} - R_{xmr}\\
  -\frac{F_{yml}}{\gamma} - R_{yml}\\
  -\frac{F_{yt}}{\gamma} - R_{yt}\\
  -\frac{F_{ymr}}{\gamma} - R_{ymr}\\
\end{pmatrix}
\]

\twocolumn
